### 2015-07-15 fundamentals/intro.tex
used multiple synonyms in various places to reduce jargon-y nature of the modular and dll terms. fixes #120

The \Cyclus nuclear fuel cycle simulator framework and its \emph{modeling
ecosystem}, the suite of agents and other physics plugins compatible with it,
incorporate modern insights from simulation science and software architecture
to solve these problems.  These modern methods simultaneously enable more
efficient, accurate, robust, and validated analysis.  This next-generation fuel
cycle simulator is the result of design choices made to:

@@

\Cyclus is a dynamic, agent-based model, which employs a modular architecture,
an open development process, discrete agents, discrete time, and arbitrarily
detailed isotopic resolution of materials. Experience in the broader field of
systems analysis indicates that agent-based modeling enables more flexible
simulation control, without loss of generality
\cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
collaboration, increases software robustness \cite{cohen_modern_2010}, and
cultivates an ecosystem of modeling options. This ecosystem is \emph{modular},
being comprised of flexible, interchangeable models of fuel cycle component
process physics that vary in their scope, depth, and fidelity. This modularity
allows users and developers to customise \Cyclus to analyze the cases that are
of interest to them, rather than any custom applicaiton the simulator was
originally developed to address.  The fundamental concepts of the \Cyclus
nuclear fuel cycle simulator capture these modern insights so that novel
challenges in nuclear fuel cycle analysis can be better addressed.

>>>>

The \Cyclus nuclear fuel cycle simulator framework and its \emph{modeling
ecosystem}, the suite of agents and other physics plug-in libraries compatible with it,
incorporate modern insights from simulation science and software architecture
to solve these problems.  These modern methods simultaneously enable more
efficient, accurate, robust, and validated analysis.  This next-generation fuel
cycle simulator is the result of design choices made to:

@@

\Cyclus is a dynamic, agent-based model, which employs a modular architecture,
an open development process, discrete agents, discrete time, and arbitrarily
detailed isotopic resolution of materials. Experience in the broader field of
systems analysis indicates that agent-based modeling enables more flexible
simulation control, without loss of generality
\cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
collaboration, increases software robustness \cite{cohen_modern_2010}, and
cultivates an ecosystem of modeling options. This ecosystem is \emph{modular},
being comprised of dynamically loadable, interchangeable, plug-in libraries of fuel cycle component
process physics that vary in their scope, depth, and fidelity. This modularity
allows users and developers to customise \Cyclus to analyze the cases that are
of interest to them, rather than any custom application the simulator was
originally developed to address.  The fundamental concepts of the \Cyclus
nuclear fuel cycle simulator capture these modern insights so that novel
challenges in nuclear fuel cycle analysis can be better addressed.
